Parameterization of the responses of subarctic European vegetation to key environmental variables for ozone risk assessment

### 2022-04-24 VegOzone.tex
finish rewriting climatology section

%Ozone
We use the bias-corrected and cross-calibrated ozone climatology \citep{ACP:Falk2021} and assess the monthly significance of the ozone concentration anomalies in 2018/19. The resulting percentage of days above/below $\pm 1\,\sigma$ is displayed for each month in Fig.~\ref{fig:anomalies_svanvik}d. Note that missing bars for months in winter and spring are both due to the temporal extent of our data and anomalies not meeting the $1\sigma$ criteria. The star indicates the reconstructed data in July. In April/May 2018, ozone was significantly elevated, while no significant enhancement is found in 2019. In both years, ozone concentrations were significantly lower than average in November. These results suggest that stagnant meteorological conditions in April/May in combination with a late start of the growing season contributed more to elevated ozone than the extensive forest fires in Sweden that did not significantly enhance \chem{\chi_{O_3}} in 2018.

In summary, 2018 had a significant number of days that were warmer, drier, and brighter than the climatology, while 2019 was a rather average year. Ozone was not significantly enhanced during the GS 2018/19, but a substantially higher number of peak \chem{\chi_{O_3}} were observed in 2018 than in 2019.

>>>>

%Ozone
We used the bias-corrected and cross-calibrated ozone climatology \citep{ACP:Falk2021} to assess the ozone anomalies in 2018/19. Note that we have not recorded ozone during winter (refer to Section~\ref{subsec:weather}). In April/May 2018, ozone was unusually elevated and stayed higher than usual through the whole GS. The highest anomaly in 2019 occurred in September at the end of the GS. The forest fires in Sweden in July enhanced ozone notably at Svanhovd.

In summary, 2018 was warmer, drier, and brighter than usual, while 2019 was a rather average year. Ozone was more enhanced in 2018 than 2019 meaning that the drought conditions in summer 2018 contributed to lower $\mathrm{POD_1}$ according to our $\mathrm{DO_3SE}$ modeling results.
